\emph{Gaia} DR2 identifies VFTS 682 as the most massive runaway star known to date

### 2018-05-16 VFTS682.tex
fixed table according to Danny's comments, added Danny's bit of text for HST description

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS 682. }
  \begin{tabular}{l|c|c}
  \tableline
\tableline
    Parameter & Value & Source\\ 
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{\emph{Gaia} DR2}\\
    DEC \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DEC}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{-0}30 $\pm$ 20 & \cite{bestenlehner:11}\\
\tableline
  \end{tabular}
  \tablecomments{\todo{the error on position is in milliarcsec, not
      degrees! Fix this, Roeland is right! Also, report relative pm,
      not absolute}}
    \end{center}
  \label{tab:vfts682}
\end{table}

@@

\section{Validation with HST proper motions}
\todo{maybe rename to Astrometry from HST and make sec. 2.1.1 or 2.2
  but above Gaia data?}
Recently, \citet{platais:18} used HST observations (based on GO-12499
\& 13359 observations with WFC3/UVIS and on archival WFPC2 and
GO-12499 with both cameras, see \citealt{platais:15}) to determine the
proper motion of massive stars in the 30 Doradus region. Our star of
interest is not saturated in any HST image \todo{?},
because of the large extinction toward this star. For
large distances ($\gtrsim50$\,kpc), HST data can compete or even
exceed Gaia data in quality.

>>>>

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS 682. }
  \begin{tabular}{l|c|c}
  \tableline
    \tableline
    Parameter & Value & Source\\
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 % $\pm$  0.03
                      & \multirow{4}{*}{\emph{Gaia} DR2}\\[5pt]
    DEC \hfill [degree] & -69.07 % $\pm$  0.05
                      & \\[5pt]
    \cline{1-2}
    $\delta\mu_\mathrm{RA}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.12$\pm$0.07 & \\[5pt]
    $\delta\mu_\mathrm{DEC}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.08$\pm$0.08 & \\[5pt]
    \hline
    $\delta\mu_\mathrm{RA}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.01$\pm$0.13 & \multirow{2}{*}{\cite{platais:18}}\\[5pt]
    $\delta\mu_\mathrm{DEC}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] &
                                                                      0.2$\pm$0.1 &
    \\[5pt]
    \hline
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & 30$\pm$20 & \cite{bestenlehner:11}\\
    \tableline
  \end{tabular}
  \tablecomments{We do not list the error on the RA and DEC positions,
    which can be retrieved from the Gaia DR2 catalog and are of order
    $\sim$$10^{-2}\,\mathrm{mas\ yr^{-1}}$. We adopt the peculiar
    radial velocity calculated using the  NV $\lambda4944$ line, which is
    less sensitive to the wind velocity structure.}
    \end{center}
  \label{tab:vfts682}
\end{table}

@@

\section{Validation with HST proper motions}
\todo{maybe rename to Astrometry from HST and make sec. 2.1.1 or 2.2
  but above Gaia data?}

Recently, \citet{platais:18} presented Hubble Space Telescope (HST)  astrometry and proper
motions in the 30 Doradus region based on two epochs of
observations; the first epoch (GO-12499; P.I.: D.~J.~Lennon)
in October 3-8 2011 and the second epoch (GO-13359) in
October 6-11 2014, both using the F775W filter.
The second epoch was designed to match the pointing and
orientation of the first epoch as exactly as possible so
that the displacement measurements could be purely differential.
While most bright massive stars (V$<$14) were saturated in
their data and missing from that catalog, due to its
high extinction, E(B-V)=0.9, this star is faint enough
to be included in that catalog. Its proper motions are
listed in \Tabref{tab:vfts682} \todo{add}. For
large distances ($\gtrsim50$\,kpc), HST data can compete or even
exceed Gaia data in quality.

% Recently, \citet{platais:18} used HST observations (based on GO-12499
% \& 13359 observations with WFC3/UVIS and on archival WFPC2 and
% GO-12499 with both cameras, see \citealt{platais:15}) to determine the
% proper motion of massive stars in the 30 Doradus region. Our star of
% interest is not saturated in any HST image \todo{?},
% because of the large extinction toward this star.
